KNNFinalYu

### 2021-05-12 DecisionTreeFinalYu.Rmd
Sampled data instead of using whole dataset for both decision tree and kNN

```{r}
stroke <- read.csv("stroke.csv")
stroke$bmi <- gsub("N/A", NA, stroke$bmi)
stroke$smoking_status <- gsub("Unknown", NA, stroke$smoking_status)
stroke <- na.omit(stroke)

@@

str(stroke)
stroke <- stroke[-c(1, 2, 3, 7, 9, 10, 11)]

stroke <- lapply(stroke, function(x) as.factor(x))

stroke <- as_tibble(stroke)

@@

```{r}
set.seed(1950)
stroke_break <- createDataPartition(stroke$stroke, times = 1, p = 0.8, list = FALSE)
training_stroke <- stroke[stroke_break,]

test_stroke <- stroke[-stroke_break,]

@@

# Baserate Calculation for Stroke
```{r}
mean(as.numeric(stroke$stroke))-1

# 0.0525394
```

# Building the Model
```{r}
set.seed(1950)
str(stroke)
as.numeric(stroke$stroke)
tree_stroke = rpart(stroke~.,  
                            method = "class",
                            parms = list(split = "gini"),
                            data = training_stroke,
                            control = rpart.control(cp=0))

>>>>

```{r}
stroke <- read.csv("stroke.csv")

stroke$bmi <- gsub("N/A", NA, stroke$bmi)
stroke$smoking_status <- gsub("Unknown", NA, stroke$smoking_status)
stroke <- na.omit(stroke)

@@

stroke_positive <- subset(stroke, stroke == 1)

stroke_negative <- subset(stroke, stroke == 0)
set.seed(1980)
stroke_sample <- stroke_negative[sample(1:nrow(stroke_negative), size = 500),]
stroke_final <- rbind(stroke_sample, stroke_positive)
stroke_final <- stroke_final[-c(1, 2, 3, 7, 9, 10, 11)]

stroke_final <- lapply(stroke_final, function(x) as.factor(x))

stroke_final <- as_tibble(stroke_final)

@@

```{r}
set.seed(1950)
stroke_break <- createDataPartition(stroke_final$stroke, times = 1, p = 0.8, list = FALSE)
training_stroke <- stroke_final[stroke_break,]

test_stroke <- stroke_final[-stroke_break,]

@@

# Baserate Calculation for Stroke
```{r}
mean(as.numeric(stroke_final$stroke))-1

# 0.4186047
```

# Building the Model
```{r}
set.seed(1950)
tree_stroke = rpart(stroke~.,  
                            method = "class",
                            parms = list(split = "gini"),
                            data = training_stroke,
                            control = rpart.control(cp=0.01))

### 2021-05-12 KNNFinalYu.Rmd
Sampled data instead of using whole dataset for both decision tree and kNN

stroke <- lapply(stroke, function(x) as.numeric(x))

@@

test_stroke <- stroke[-stroke_break,]
```
```{r}
chooseK = function(k, train_set, val_set, train_class, val_class){
  set.seed(1)
  class_knn = knn(train = train_set,
                  test = val_set,
                  cl = train_class,
                  k = k,
                  use.all = T)
  conf_mat = table(class_knn, val_class)
  accu = sum(conf_mat[row(conf_mat) == col(conf_mat)]) / sum(conf_mat)
  cbind(k = k, accuracy = accu)
}

>>>>

stroke_positive <- subset(stroke, stroke == 1)

stroke_negative <- subset(stroke, stroke == 0)
set.seed(1980)
stroke_sample <- stroke_negative[sample(1:nrow(stroke_negative), size = 500),]
stroke_final <- rbind(stroke_sample, stroke_positive)

stroke <- lapply(stroke_final, function(x) as.numeric(x))

@@

test_stroke <- stroke[-stroke_break,]
```

```{r}
chooseK = function(k, train_set, val_set, train_class, val_class){
  set.seed(1)
  class_knn = knn(train = train_set,
                  test = val_set,
                  cl = train_class,
                  k = k,
                  use.all = T)
  conf_mat = table(class_knn, val_class)
  accu = sum(conf_mat[row(conf_mat) == col(conf_mat)]) / sum(conf_mat)
  cbind(k = k, accuracy = accu)
}
